A multi-scale story of the diffusion of a new technology: the web

### 2024-06-11 presentations/web_diffusion.Rmd
path

# load 2000 co.uk
# path.2000 <- "C:/Users/nw19521/OneDrive - University of Bristol/projects/archive/nuts/all2000couk.csv"
path.2000 <- "/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/all2000couk.csv"

>>>>

# load 2000 co.uk
# path.2000 <- "C:/Users/nw19521/OneDrive - University of Bristol/projects/archive/nuts/all2000couk.csv"
# path.2000 <- "/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/all2000couk.csv"
path.2000 <- paste0(path, "/data/temp/all2000couk.csv")
